\vspace{0.3cm}

\begin{itemize}

	\item[${\textbf{[G1]}}$] {\textbf{Allows a person to register and to have a personal area to which he/she can access with his/her credentials.}
		\begin{itemize}
			\item[$\textbf{[R1]}$] {A person can register in the application by providing his/her personal data, a unique e-mail and a password.}
			\item[$\textbf{[D1]}$] {The user has a device linked to his/her smartphone.}
			\item[$\textbf{[R2]}$] {A user can log in by providing his/her e-mail and password.}
			\item[$\textbf{[R3]}$] {Each user has a personal area associated with his/her credentials.
				\begin{itemize}
					\item[$\textbf{[R3.1]}$] {A user can see the third parties subscribed to his/her data in his/her personal area.}
					\item[$\textbf{[R3.2]}$] {A user can add weight and height in his/her personal area.}
					\item[$\textbf{[R3.3]}$] {A user can link his/her device to the app in his/her personal area.}
				\end{itemize}}
		\end{itemize}}


	\item[${\textbf{[G2]}}$] {\textbf{Allows the third party to register and to have a personal area to which it can access with his/her credentials.}
		\begin{itemize}
			\item[$\textbf{[R4]}$] {A third party can register in the application by providing his/her third party data, a unique e-mail and a password.}
			\item[$\textbf{[R5]}$] {A third party can log in by providing his/her e-mail and password.}
			\item[$\textbf{[R6]}$] {Each third party has a personal area associated with his/her credentials.
				\begin{itemize}
					\item[$\textbf{[R6.1]}$] {A third party can see the data of users and groups of users obtained from his/her personal area.}
					\item[$\textbf{[R6.2]}$] {A third party can require data to users or groups of users from his/her personal area.}
				\end {itemize}}
		\end{itemize}}


	\item[${\textbf{[G3]}}$] {\textbf{Allows the third party to require data.}
		\begin{itemize}
			\item[$\textbf{[D2]}$] {The user's smartphone can provide an accurate enough current location.}
			\item[$\textbf{[D3]}$] {The user's device can provide accurate enough healt parameters.}
			\item[$\textbf{[D4]}$] {The user's smartphone can provide constantly data to \hbox{\emph{D4H}}.}
			\item[${\textbf{[G3.1]}}$] {\textbf{Third party can require single person's data.}
				\begin{itemize}
					\item[$\textbf{[R7]}$] {A third party can require user's data by providing his/her fiscal code and the reason of the request.}
				\end{itemize}}
			\item[${\textbf{[G3.2]}}$] {\textbf{Third party can require anonymized data of group of people.}
				\begin{itemize}
					\item[$\textbf{[R8]}$] {A third party can require anonymized data of groups of users by providing constraints that define users.
						\begin{itemize}
							\item[$\textbf{[R8.1]}$] {The group of user to which require data can be specified by any combination of geographic areas, range of ages, 									sex, range of weights and range of heights.}
							\item[$\textbf{[R8.2]}$] {Requests of data related  to groups of users are accepted by \hbox{\emph{TrackMe}} if and only if the amount of 									users which respect the given constraints is equal or grater than 1000.}
						\end{itemize}}
				\end{itemize}}
		\end{itemize}}


	\item[${\textbf{[G4]}}$] {\textbf{Allows the user to accept or not to let a third party to have access to his/her/her data.}
		\begin{itemize}	
			\item[$\textbf{[R9]}$] {A user is notified by the \hbox{\emph{D4H}}'s app when a third party makes a request to have access to the user's data.}
			\item[$\textbf{[R10]}$] {A user can reply to a third party interested to his/her data from his/her personal area within 30 days.}
		\end{itemize}}


	\item[${\textbf{[G5]}}$] {\textbf{Allows third party to subscribe for new data.}
		\begin{itemize}
			\item[$\textbf{[R11]}$] {After a request has been accepted, the third party can decide to subscribe to the data of that user or group of users.}
			\item[$\textbf{[R12]}$] {A user is notified by the \hbox{\emph{D4H}}'s app when a third party decides to subscribe for his/her data.}
			\item[$\textbf{[R13]}$] {A user can stop the subscribe to his/her data by a third party in any moment from his/her personal area.}
			\item[$\textbf{[R14]}$] {If a user stops the subscribe of a third party to his/her data, the third party will be notified by the \hbox{\emph{D4H}}'s app.}
		\end{itemize}}


	\item[${\textbf{[G6]}}$] {\textbf{Allows third party to see users' or groups of users' data obtained through a successful request.}
		\begin{itemize}
			\item[$\textbf{[R15]}$] {Third parties can see the obtained data directly on their personal area.}
			\item[$\textbf{[R16]}$] {Third parties are notified by the \hbox{\emph{D4H}}'s app if their's request for new data has been rejected.}
		\end{itemize}}

	\item[${\textbf{[G7]}}$] {\textbf{Allows users to monitor their healt parameters.}}
		\begin{itemize}
			\item[$\textbf{[R20]}$] {A user can see his/her health parameters in his/her personal area.}
		\end{itemize}

	\item[${\textbf{[G8]}}$] {\textbf{Allows users to activate or deactivate the \hbox{\emph{ASOS}} service on top of \hbox{\emph{D4H}}.}
		\begin{itemize}
			\item[$\textbf{[R17]}$] {Users can activate or deactivate the \hbox{\emph{ASOS}} service from their's personal area.}
		\end{itemize}}


	\item[${\textbf{[G9]}}$] {\textbf{Allows an unhealty user to receive quick help if have the \hbox{\emph{ASOS}} service activated on his/her account.}
		\begin{itemize}
			\item[$\textbf{[D5]}$] {There is an SOS service that has the capability to receive emergency calls by \hbox{\emph{ASOS}}.
				\begin{itemize}
					\item[$\textbf{[D5.1]}$] {The SOS service has the capability to receive data about the unhealty user.}
					\item[$\textbf{[D5.2]}$] {The SOS service has the capability to send assistance to the unhealty user.}
				\end{itemize}}
			\item[$\textbf{[R18]}$] {ASOS is able to contact the SOS service in case of the rise of an unhealty user in 5s.}
			\item[$\textbf{[R19]}$] {ASOS is able to send to the SOS service the unhealty user's data and personal data.}
		\end{itemize}}
\end{itemize}

\subsection{Use Cases}
\input{./Specific_Requirements/use_cases.tex}
\subsection{Sequence Diagrams}
\input{./Specific_Requirements/sequence_diagrams.tex}