\subsection{Scenario 1}
Matteo bought a new smart watch which is compatible with his smartphone and, because of this, he would like to download on his phone an application to monitor his health parameters. 
A friend of him recommended the \textit{D4H} and \textit{ASOS} app and Matteo immediately downloaded it. After he registered himself by giving some personal data, his email and by choosing a password he added some information in settings:
\begin{itemize}
	\item {Matteo inserted his weight and height;}
	\item {he linked his smart watch to the smarphone throw the application to obtain the health parameter;}
\end{itemize}
Then he accepted to activate the \textit{ASOS} service by going in the \textit{ASOS} are in the main menu.
Matteo started to use this application and now he can constantly check his health parameters and see all third parties which has required and which use his data.

\subsection{Scenario 2}
The Health-Tech society would like to obtain data of group of users to analyze and to do some inference on them without spend money to develop a software to collect data from users.This society decides to download the \textit{D4H} application.
After the registration done by giving some personal data, e-mail and a chosen password Health-Text logins to his personal area and can start to require data of a group of users. To require those data the society puts some constraint to obtain data of a specific group of users:
\begin{itemize}
	\item {users must have an age between 20 and 30;}
	\item {users can be both male or female;}
	\item {the society wants to analyze data of users with a weight between 50 kg and 70 kg;}
	\item {users must have a height between 160 cm and 180 cm;}
	\item {they must live in Lombardy;}
\end{itemize}
After a while the app notifies that the request has been accepted because the number of users that respect the constraints is higher than the treshold applied to guarantee the users' privacy.
%The society also subscribes to receive other data of this group of users.

\subsection{Scenario 3}
The Health-Tech society would like to obtain data of a group of users to analyze them. It specifies those constraints for the group of users:
\begin{itemize}
	\item {users must have an age between 16 and 18;}
	\item {users must be male;}
	\item {the society wants to analyze data of users with a weight heigher than 100 kg;}
	\item {users must have a height between 160 cm and 180 cm;}
	\item {they must live in Sondrio;}
\end{itemize}
After a while the app notifies that the request has been denied because the number of users which respect the constraints is smaller than the treshold applied to guarantee the users' privacy. 

\subsection{Scenario 4}
The Health-Tech society would like to provide some personalized services to a user. An employee enters in the society's  \textit{D4H} personal area and does a request for obtaining the specific user's data. 
To do it Health-Tech must have a NumberId related to the user or it must have his/her fiscal code and it must explain the reason why it is requiring those data. After a while the app notify that the user has accepted the request and so the society starts to receive data and subscribes for obtaining new data from the user.\\
The app constantly sends the user's data to the Health-Tech personal area.

\subsection{Scenario 5}
The Health-Tech society would like to provide some personalized services to a user. An employee enters in the society's  \textit{D4H} personal area and does a request for obtaining the specific user's data. 
To do it Health-Tech must have a NumberId related to the user or it must have his/her fiscal code and it must explain the reason why it is requiring those data. After a while the app notify that the user didn't accept the request; the request is delated and the employee close the app.

\subsection{Scenario 6}
Diana is at university when the \textit{D4H} and \textit{ASOS} app sends her a notification requiring to accept or deny the possibility to shere her data to a third party.
She has chosen to deny it because she was not interested in the proposed service.

\subsection{Scenario 7}
Edoardo is at work when the \textit{D4H} and \textit{ASOS} app sends her a notification requiring to accept or deny the possibility to shere her data to a third party.
She has chosen to accept it bacause she is interested in the proposed service. As soon as she has accepted she goes in the menu and enters in the area which shows all third parties. She can see that the new one has been added immediately.

\subsection{Scenario 8}
Rosaria is walking around the street, she is going to take a coffee with her niece when she has an heart attack. Fortunately she is dressing up her smart watch which takes over that her health parameters are lower than the threshold. The app contacts the SOS service and sends to it Rosaria's personal details and data and her location in less than 5 seconds from the detaction. The SOS service immediately sends her an ambulance which brings her to the hospital in time to save her.
