In this section are specified the major function of the \textit{TrackMe}'s system according to the presented goals.
\begin {itemize}
	\item {\textbf{Request data to users}\\ Third parties must be able to request data directly to the users if and only if they can provide to the app the fiscal code or the social security number of the user and the reason why they would like to see the user's parameters. The requestes about single users can be done in the apposite area of third parties' app. \\ When a user receives a request for his data, he must be able to reply positively or negatively selecting the relative icon on the data request notification which contains the reason of the request . \\ Data collected throught a successfully request will be shown in a graph representing the trend of the user's health rate along the current day, week, month and year in the area of third parties' app about collected data. }

	\item {\textbf{Request data to groups of users}\\ Third parties must be able to request data of groups of users to \textit{D4H}. The groups of users must be specified by selecting the range of age, weight, height and address in which the third parties are interested. The requestes about groups of users can be done in the apposite area of third parties' app.  \\ The requestes about groups of users must be take in charge by \textit{D4H} which will procede to guarantee the data only if the users who respect the ranges specified by the third parties are more than 1000. \\ Data of groups of users received by third parties must be strictly anonymized. \\ Data collected throught a successfully request will be shown in a graph representing the trend of the users' health rate along the current day, week, month and year in the area of third parties' app about collected data.}

	\item {\textbf{Subscription service}\\ Third parties must be able to subscribe to new data of users or groups of users after a successfully request for his/them data by selecting the apposite icon on the data request accepted notification. \\ Third parties subscribed to new data of users or groups of users will receive them as soon as they are produced and can be seen in the area of third parties' app about collected data.}

	\item {\textbf{Monitor health parameters}\\ Users must be able to check their health parameters in real time. Those parameters will be shown in the apposite area of the users' app in a graph representing the trend of the users' health rate along the current day, week, month and year; in this area will be also possible to see the weight and height parameter set by the user. }

	\item {\textbf{Medical assistance service}\\ Users must be able to activate or deactivate the \textit{ASOS} service on their account by the \textit{ASOS} area of the users' app. \\ Users with the \textit{ASOS} service activated on their account will have a guaranteed tempestive medical assistance in case of drop of their health parameters below a certain threshold. The medical assistance is guaranteed to be informed about the unhealty user in a maximum of 5 seconds from the drop of the user's health parameters. \textit{TrackMe} will give to the SOS service in charge of the medical assistance the location, the health parameters and the personal data of the unhealty user to guarantee the best possible service.}
		

\end {itemize}