\subsection{Definitions}
	\begin{itemize}
		%def related to the software
		\item{\textbf{TrackMe's system:} the whole software, it's a compact way to refer to all different services that must be 					developed.}

		%def related to devices
		\item {\textbf{Smartphone:} HW that runs the app and the location service.}
		\item {\textbf{Device:} HW that collects all user's health parameters.}

		%def related to data
		\item {\textbf{Personal data:} name, surname, date of birth, address, fiscal code and sex of an individual.}
		\item {\textbf{Third party data:} name, type of society, p. iva, fiscal code, address.}
		\item {\textbf{Data:} location and health parameters collected by the user's device.}
		\item {\textbf{Location:} real time GPS position.}
		\item {\textbf{Health parameters:} data about the user's health status collected by his/her device, such as heart beat, 						vein pressure, body temperature ..}

		%def related to users
		\item {\textbf{User:} an individual user of the application who provides data.}
		\item {\textbf{Third party:} somebody that uses the application because interested in obtaining data of users or groups of users.} 
		\item {\textbf{Unhealty user:} user who has health parameters below a certain treshold.}
		\item {\textbf{Credentials:} the unique couple of e-mail and password associated to each user or third part.}

		%def of outside services
		\item{\textbf{SOS service:} the service contacted to send help to the user in case of health parameters below tresholds.}
	\end {itemize}

\subsection{Acronyms}
	\begin{itemize}
		\item {\textbf {RASD:} Requirement Analysis and Specification Document.}
		\item {\textbf {GPS:} Global Positioning System.}
		\item {\textbf {HW:} hardware.}
		\item {\textbf {API:} Application Programming Interface.}
		\item {\textbf {D4H:} Data4Help.} 
		\item {\textbf {ASOS:} AutomatedSOS.}
	\end{itemize}

\subsection{Abbreviations }
	\begin{itemize}
		\item {\textbf{[Gn]:} n-th goal}
		\item {\textbf{[Dn]:} n-th domain assumption}
		\item {\textbf{[Rn]:} n-th requiremnt}
		\item{\textbf{App:} appllication}
	\end{itemize}


