\vspace{0.3cm}

\begin{itemize}

	\item[${\textbf{[G1]}}$] {\textbf{Allows the user to register and to have a personal area to which he/she can access with a secure code.}
		\begin{itemize}
			\item[$\textbf{[R1]}$] {A person can register in the application by providing his personal data, a unique e-mail and a password.}
			\item[$\textbf{[D1]}$] {The user has a device linked to his smartphone.}
			\item[$\textbf{[R2]}$] {A user can log in by providing his e-mail and password.}
			\item[$\textbf{[R3]}$] {Each user has a personal area associated with his credentials.
				\begin{itemize}
					\item[$\textbf{[R3.1]}$] {A user can see his health parameters in his personal area.}
					\item[$\textbf{[R3.2]}$] {A user can see the third parties subscribed to his data in his personal area.}
				\end{itemize}}
		\end{itemize}}


	\item[${\textbf{[G2]}}$] {\textbf{Allows the third party to register and to have a personal area to which it can access with a secure code.}
		\begin{itemize}
			\item[$\textbf{[R4]}$] {A third party can register in the application by providing his third party data, a unique e-mail and a password.}
			\item[$\textbf{[R5]}$] {A third party can log in by providing his e-mail and password.}
		\end{itemize}}


	\item[${\textbf{[G3]}}$] {\textbf{Allows the third party to require data.}
		\begin{itemize}
			\item[$\textbf{[D2]}$] {The user's smartphone can provide an accurate enough current location.}
			\item[$\textbf{[D3]}$] {The user's device can provide accurate enough healt parameters.}
			\item[$\textbf{[D4]}$] {The user's smartphone can provide constantly data to D4H.}
			\item[$\textbf{[R6]}$] {A third party can require user's personal data by providing his fiscal code and the reason of the request.}
			\item[$\textbf{[R7]}$] {A third party can require anonymized personal data of groups of users by providing a range of users.
			\begin{itemize}
				\item[$\textbf{[R7.1]}$] {The range of user to which require data can be specified by any combination of geographic coordinates and range of ages.}
			\end{itemize}}
		\end{itemize}}


	\item[${\textbf{[G4]}}$] {\textbf{Allows the user to accept or not to let a third party to have access to his/her data.}
		\begin{itemize}	
			\item[$\textbf{[R8]}$] {A user is notified when a third party makes a request to have access to the user's personal data.}
		\end{itemize}}


	\item[${\textbf{[G5]}}$] {\textbf{Allows third party to subscribe for new data.}
		\begin{itemize}
			\item[$\textbf{[R9]}$] {A user is notified when a third party decides to subscribe for his data.}
		\end{itemize}}


	\item[${\textbf{[G6]}}$] {\textbf{Allows third party to obtain the required data if the request has been accepted, a notification if it has been refused.}
		\begin{itemize}
			\item[$\textbf{[R10]}$] {Third parties receive personal data of users through the given e-mail.}
		\end{itemize}}


	\item[${\textbf{[G7]}}$] {\textbf{Allows an unhealty user to receive quick help.}
		\begin{itemize}
			\item[$\textbf{[D5]}$] {There is an SOS service that has the capability to receive emergency calls by AutomatedSOS.}
			\item[$\textbf{[R1]}$] {ASOS is able to contact the SOS service in case of the rise of an unhealty user in 5s.}
			\item[$\textbf{[R2]}$] {ASOS is able to send to the SOS service the unhealty user's data.}
		\end{itemize}}


\end{itemize}